Self-interacting dark matter model without dark energy in cosmology

### 2024-12-02 article/article.tex
function has stiff point depend on the value of logkC1

   To constrain the relevant IDM models (\cite{refId0}), we use the newly revised
   observational $H(z)$ data (OHD)(\cite{Zhang_2014};\cite{PhysRevD.71.123001};
   \cite{Daniel.Stern_2010};\cite{M.Moresco_2012};\cite{Moresco_2016};
   \cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};\cite{Borghi_2022};
   \cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia (\cite{Scolnic_2022}), the CMB data from
   Planck 2018 and the BAO data from SDSS and DESI 2024.

@@

   We use the fiducial SN Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
   host distances(\cite{Riess_2022}), which gives the $\mu_\text{data}$ and constrains $H_0$
   in advance. To eliminate the influence of $M_b$, we give the likelihood function
   as \begin{equation}
      \chi_{\text{S}}^2=A-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
   \end{equation}
   where $A=\sum_{i=1}^{1701}(\mu_{\text{th}}-\mu_{\text{data}})^2/\sigma_i^2,
   B=\sum_{i=1}^{1701}(\mu_{\text{th}}-\mu_{\text{data}})/\sigma_i^2,C=\sum_i^{1701}1/\sigma_i^2$,
   the distance modulus is $\mu=5\log_{10}(d_L/\text{Mpc})+25$, and the
   luminosity distance $d_L$ can be given as a function of redshift $z$
   \begin{equation}
      d_L=(1+z)\int_0^z\frac{c\mathrm{d}z'}{H(z')}.
   \end{equation}
   However, the Eq.(\ref{eq:9}) just need the $H_0$ to caculate the $M_x$
   and we would still use the simple likelihood function as
   \begin{equation}
      \chi_{\text{SNe}}^2=A=\sum_{i=1}^{1701}\frac{(\mu_{\text{th}}-\mu_{\text{data}})^2}{\sigma_i^2}.
   \end{equation}
   Apparently these two functions give the same constraints in $\Omega_{2,0}$
   and $\kappa C_1$.

@@

\subsection{Cosmic Microwave Background}

   We adopt the $\Omega_bh^2$ from BBN,
   give the constraint to $r_d$

>>>>

   To constrain the relevant IDM models (\cite{refId0}), we use the newly revised
   observational $H(z)$ data (OHD)(\cite{Zhang_2014};\cite{PhysRevD.71.123001};
   \cite{Daniel.Stern_2010};\cite{M.Moresco_2012};\cite{Moresco_2016};
   \cite{10.1093/mnras/stx301};\cite{10.1093/mnrasl/slv037};\cite{Borghi_2022};
   \cite{Jiao_2023}),the Pantheon+ set of 1701 SNe Ia (\cite{Scolnic_2022}),
   the BAO data from SDSS and DESI 2024.

@@

   We use the fiducial SN Ia magnitude ($M_b$) determined from SH0ES 2021 Cepheid 
   host distances(\cite{Riess_2022}), which gives the $\mu_\text{data}$ and constrains $H_0$
   in advance. To eliminate the influence of $M_b$, we give the likelihood function
   as \begin{equation}
      \chi_{\text{SNe}}^2=A-\frac{B^2}{C}+\ln\left(\frac{C}{2\pi}\right),
   \end{equation}
   where $A=\sum_{i=1}^{1701}(\mu_{\text{th}}-\mu_{\text{data}})^2/\sigma_i^2,
   B=\sum_{i=1}^{1701}(\mu_{\text{th}}-\mu_{\text{data}})/\sigma_i^2,C=\sum_i^{1701}1/\sigma_i^2$,
   the distance modulus is $\mu=5\log_{10}(d_L/\text{Mpc})+25$, and the
   luminosity distance $d_L$ can be given as a function of redshift $z$
   \begin{equation}
      d_L=(1+z)\int_0^z\frac{c\mathrm{d}z'}{H(z')}.
   \end{equation}
   However, the Eq.(\ref{eq:9}) just need the $H_0$ to caculate the $M_x$
   and we would still use the simple likelihood function as
   \begin{equation}
      \tilde{\chi}_{\text{SNe}}^2=A=\sum_{i=1}^{1701}\frac{(\mu_{\text{th}}-\mu_{\text{data}})^2}{\sigma_i^2}.
   \end{equation}
   Apparently these two functions give the same constraints in $\Omega_{2,0}$
   and $\kappa C_1$.

@@
